\titleformat{\chapter}[display]
  {\normalfont\Large\bfseries\centering}
  {\chaptertitlename\ \thechapter}{0pt}{\Huge}
\chapter{INTERNSHIP DETAILS}
\thispagestyle{fancy}

\section{Full Stack Devlopment} Full-stack web development is a subset of web development that encompasses all of the responsibilities involved in creating 
websites for intranet or internet hosting.It helps to find out a perfect solution for all the front-end, testing, mobile application back-end, etc. full-stack developer work on all this, and also it will take care of the entire procedure of a project.
\section{Problem Statement} At Caygnus, we specialize in creating cutting-edge IT solutions that drive business success. Our passion for technology fuels our drive to deliver transformative software. our internship program offers you the opportunity to work on live, real-world projects, giving you valuable experience in the IT industry.Interns undergo a structured placement assessment, designed to evaluate performance and skill set, helping to prepare for future opportunities in the tech industry.Our program is designed to foster career development and provide the foundation for success in the ever-evolving IT landscape.we have identified tasks for interns to complete during their internship:
1. Portfolio Website: intern’s current portfolio lacks structure, visual coherence, and fails to effectively showcase their skills, projects, and achievements. As a crucial tool for personal branding and professional networking, a well-crafted portfolio website is essential to showcase the intern’s capabilities and accomplishments to potential employers and clients.\bigskip
\newline \textbf{1.Portfolio website:} Showcasing the intern’s skills, projects, and achievements. The portfolio website should serve as a professional showcase of the intern’s capabilities in web development, highlighting their proficiency in coding languages, frameworks, and design principles. This task will not only allow interns to demonstrate their creativity and technical expertise but also serve as a valuable asset for future career opportunities.
\newline \textbf{2.To-do List application:}  Create the basic structure of the to-do list UI by adding an input field for adding tasks, a button to submit, and a dynamic list to display tasks. Use the `useState` hook to store the current task input and list of tasks.Focus on handling form input, managing a list of tasks with `useState`, and rendering dynamic content. Do not focus on advanced topics like conditional rendering or context APIs yet.\smallskip
\newline \textbf{3.Weather app using API} :Learn how to make an API call to a public API using `fetch()`. You will retrieve data and display it on the page.Focus on understanding how to make simple API requests and handle JSON responses. Avoid advanced concepts like error handling with `catch()` or using libraries like Axios for now.\smallskip
\newline \textbf{4.Calculator Application:}  Develop a calculator application that allows users to
perform basic mathematical operations such as addition, subtraction, multiplication, and division. The calculator should be intuitive, user-friendly, and visually appealing, providing a seamless user experience across different devices andscreen sizes. This task will test interns’ ability to implement functionality using JavaScript or other programming languages while adhering to best practices in web development. 
\section{Objectives}
\begin{enumerate}
\item Hands-on Learning:-Gain practical experience by working on real-world webdevelopment projects under the guidance of experienced mentors.\smallskip
\item Mentorship from Experts:-Work closely with industry professionals who provide guidance, feedback, and support to help you develop both technical and softskills.\smallskip
\item Skill Development:-Enhance proficiency in programming languages, frameworks, and tools commonly used in web development, such as HTML, CSS, JavaScript, and popular frameworks like React.js.\smallskip
\item Placement Assessment:-In order to analyze their performance and skill set and get ready for future prospects in the tech sector, interns go through a placement exam.\smallskip
\item  Problem-Solving:- Develop problem-solving skills by troubleshooting issues, debugging code, and finding innovative solutions to technical challenges encountered during the development process
\end{enumerate}

	
